%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[a4paper]{mcdowellcv}



% Set applicant's personal data for header
\name{Erika Musterfrau}
% alternative to the following: Set \address{} and \city{}. City is needed for Signature Line
\city{Berlin}
\country{Germany}
\personallinks{ 
\link{https://github.com/ErikaMusterfrau}{GitHub}, \link{https://www.linkedin.com/in/erika_musterfrau/}{LinkedIn}}

\contacts{
+49 123 456 789 00 \linebreak 
\link{mailto:erika@musterfrau.com}{erika@musterfrau.com}}

\begin{document}
	
    \makeheader

    % Skills
    \begin{cvsection}{}
    \begin{multicols}{2}
        \begin{itemize}
            \item some nice skills
            \item and some more 
            %
            \item Python (4+ years), Java (4+y)
            \item PyTorch, Pandas, etc
        \end{itemize}
    \end{multicols}
        
    \end{cvsection}
    
    \begin{cvsection}{Section with Itemization}
        \begin{cvitemize}
            {Left}
            {Center Heading}
            {Right}
                \cvitem{\texttt{CVItem} of arbitrary length. May be plain text or    
                      \begin{itemize}
                        \item sub-items
                        \item and one more.
                    \end{itemize}
                    }
                    [Remark]
                    [List of Keywords]
                \cvitem{Only content is mandatory.}[][]
                \cvitem{Further information without remark.}[][some nice skills]
                \cvitem{You can \highlight{highlight} certain aspects.}[][]
        \end{cvitemize}
    \end{cvsection}

    \begin{cvsection}{Section with Subsections and Keywords}
        \begin{cvkeywordsubsection}
            {Left}
            {Center Heading}
            {Right}
            {keywords}
                 This is a \texttt{CVKeywordSubsection} Environment. 
                 The main differences in the environments are that \texttt{CVKeywordSubsection} takes a list of keywords, \texttt{CVSubsection} does not handle keywords nor offers the keyword margin.
                 Further, \texttt{CVKeywordSubsection} has the list of keywords for the entire section, while \texttt{cvitem} has list of keywords per bullet point.
        \end{cvkeywordsubsection}
        %
        \begin{cvkeywordsubsection}
            {Only left is mandatory.}
            {}
            {}
            {}
            But still the page is split into content and keyword parts as we can see if we write enough text so that it stretches over more than one line. 
        \end{cvkeywordsubsection}
        %
    \end{cvsection}

    \begin{cvsection}{Section with Subsections without Keywords}
        \begin{cvsubsection}{Left}{Center Heading}{Right}
            Content that stretches over entire pages without the keyword margin. Use whenever you like but probably aesthetically best when choosing either \texttt{cvsubsection} or \texttt{cvkeywordsubsection} for entire document.
            
        \end{cvsubsection}
                   
    \end{cvsection}

\addSignature

\end{document}
